\documentclass[a4paper,11pt]{article}
\usepackage[style=numeric,natbib=true,sorting=none,maxbibnames=99]{biblatex}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{url}
\bibliography{references.bib}

\begin{document}
\title{Analyzing Tor Artifacts in Memory \\~\\
\large{Cyber Crime and Forensics \\
Master Security and Network Engineering\\  University of Amsterdam\\
Project report\\}
\textbf{Version:} 1.0}
\author{
    Axel Koolhaas \texttt{a.e.koolhaas@student.vu.nl} \and
    Alexandros Dimos \texttt{a.dimos@student.vu.nl}\\
    \\
}
\date{
    \textnormal \today
}
\maketitle

\clearpage

\input{tex/1_abstract.tex}
\clearpage

\tableofcontents
\clearpage

\section{References}
It was possible to reconstruct video content played in Chrome web browser by using
locally buffered cache data on the hard drive.
\cite{horsman2018reconstructing}

Both Mozilla Firefox and Google Chrome hard drive cache researched to
prove that somebody watched images. Testing has highlighted inconsistent cache
behaviour, meaning that it may not possible to make an accurate
assumption of which images were viewed by a user based on cached
content alone.
\cite{horsman2018didn}

Research on artifacts left behind by private browser modes. All large
web browsers were researched, e.g. Chrome, Firefox and
Safari. Majority of important artifacts with regard to privacy are
removed by the browsers, but users did not take into account the
impact of artefacts with low or medium valuation being left behind
\cite{tsalis2017exploring}. One of mitigations presented in this paper
is storing data into the RAM. This decreases the chance of
confidential data leaks. However, as we present in our paper, forensic
experts can still extract artifacts from RAM.

Research where they managed to recover artifacts from private browsing
sessions from RAM. \cite{yang2017applying}

\input{tex/2_introduction.tex}
\input{tex/3_related_work.tex}
\input{tex/4_methods.tex}
\input{tex/5_implementation.tex}
\input{tex/6_results.tex}
\input{tex/7_discussion.tex}
\input{tex/8_conclusion.tex}
\printbibliography

\end{document}
